Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-04-23 manuscript.tex
readme update

\author{
  Myeongseok Ryu, Donghwa Hong, and Kyunghwan Choi
\thanks{
    Myeongseok Ryu, Donghwa Hong and Kyunghwan Choi are with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: \{dding\_98, ???, khchoi\}@gist.ac.kr).

@@

%% Abstract
\begin{abstract}
  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for weight norm and convex input constraints. 
  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, while addressing both types of constraints. 
  The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. 
  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. 
  Real-time implementation was conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
\end{abstract}

@@

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in\{1,\cdots,n\},j\in\{1,\cdots ,m\}
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix, and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

>>>>

\author{
  Myeongseok Ryu, Donghwa Hong, and Kyunghwan Choi
\thanks{
    Myeongseok Ryu is with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: dding\_98@kaist.ac.kr).

    Donghwa Hong is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: ???@gist.ac.kr).

    Kyunghwan Choi is with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: khchoi@kaist.ac.kr).

@@

%% Abstract
\begin{abstract}
  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for weight norm and convex input constraints. 
  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, while addressing both types of constraints. 
  The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. 
  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. 
  The proposed controller was validated via real-time implementation conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
\end{abstract}

@@

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in\{1,\cdots,n\},j\in\{1,\cdots ,m\}
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= \left(\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  \right)^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix, and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}
